---
title: "Introduction to simplerfit"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{simplerfit-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(simplerfit)
```

## Brief Introduction
Simplerfit is function that will help reduce effort in section of a model building pipeline. There are six functions that are included in this R package which are described in more detail below. Seasoned and amateur data scientists' can use this package in their pipelines to make the task more efficient.

This document introduces you to simplerfit's functions and how to use them.

## Data
To explore the basic functionality of simplerfit, the dataset `gapminder`. If you want to vizualise the data, before going through the functions, use the code below to load it.

```{r}
# load gapminder dataset
gapminder <- gapminder::gapminder
head(gapminder)
```

## Function Demonstration

### Cleaning the dataframe
The cleaner function does the basic cleaning of a raw data-frame by removing the empty rows, stripping extra white spaces in the data and converting the column names to lower case. 
```{r}
clean_df <- clean_data(gapminder::gapminder)
```

### EDA
The functions take in the cleaned data set to create a correlation plot and a distribution plot.
```{r}
plot_corr(clean_df, corr = 'pearson', pair_cols=c('lifeexp', 'pop', 'gdppercap'))

plot_distributions(clean_df, bins = 30, hist_cols=c("gdppercap", "pop"), density=TRUE)
```

### Regression
If the problem is of a regression nature, the RMSE scores of dummy regressor, linear regressor and ridge are compared
```{r fig.width=7, fig.height=4}
fit_regressor(clean_df, 
              target_col="gdppercap", 
              numeric_feats=c("year", "lifeexp", "pop"), 
              categorical_feats <- c("continent"), 
              cv =5)
```

### Classification
If the problem is of a classification nature, the accuracy scores of dummy classifier and logistic regression are compared
```{r}
clean_df <- clean_df |> dplyr::filter(continent=="Asia" | continent=="Europe")
clean_df$country <- as.character(clean_df$country)
clean_df$continent <- as.character(clean_df$continent)
clean_df$year <- as.numeric(clean_df$year)
clean_df$pop <- as.numeric(clean_df$pop)

fit_classifier(clean_df, 
               target_col = 'continent', 
               numeric_feats = list('gdppercap'), 
               categorical_feats = list('country'), 
               cv = 5)
```

